My catchy title for a manuscript

### 2017-12-12 code.Rmd
new figures

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(here)
library(readxl)
library(viridis)
library(ggthemes)
library(lme4)
library(cowplot)
library(broom)
library(agricolae)
library(lattice)
library(influence.ME)
```

@@

```{r message=FALSE, warning=FALSE}
library(car)
Anova(glmm_per)
```

@@

```{r}
library(lattice)
plot(glmm_per, type = c("p", "smooth"))
qqmath(glmm_per, id = 0.05)
```

@@

```{r message=FALSE, warning=FALSE}
library(emmeans)
medias <- emmeans(glmm_per, ~ species_genotype * substrate)
med <- cld(medias, Letters = LETTERS, alpha = .05)

@@

This new `med` dataframe does not contain the two original variables we want to use to plot the data. Let's separate the `species_genotypes` variable and create `genotype` and `species`.

@@

```{r message=FALSE, warning=FALSE}
Sys.setlocale("LC_ALL", "pt_BR.UTF-8")
mgr <- read_excel(here("data", "all-data.xlsx"), "mycelia")

@@

```{r}
# 15 C
mgr15 <- mgr %>%
  filter(temperature == "15 °C")

@@

# 30 C
mgr30 <- mgr %>%
  filter(temperature == "30 °C")

@@

```{r message=FALSE, warning=FALSE}
library(scales)
spor1 <- spor %>%
  group_by(species, genotype, isolate) %>%
  summarize(mean_spor = mean(spores_ml))
spor2 <- spor1 %>%
  ggplot(aes(genotype, mean_spor, color = species)) +
  geom_jitter(width = 0.1, size = 3) +
  theme_few() +
  scale_color_viridis(discrete = TRUE) +
  theme(legend.position = c(1, 5), axis.text.x = element_text(angle = 0, hjust = 0.5, size = 7), legend.text = element_text(size = 7, face = "italic"), axis.title = element_text(size = 8)) +
  labs(x = "", y = "Macroconidia count (x 10.000)", color = "Species") +
  ylim(0, 5) +
  guides(colour = guide_legend(nrow = 2))
```

@@

grid5 <- plot_grid(mgr1, grid1, labels = c("A"), rel_heights = c(1, 1), ncol = 1, align = "hv")
ggsave(here("figs", "figure3.png"), grid5, width = 5, height = 5)

@@

@@

audpc_194 %>%
  group_by(species, genotype) %>%
  summarize(
    mean_audpc = mean(audpc),
    sd_audpc = sd(audpc)
  ) %>%
  ggplot(aes(species, mean_audpc, color = genotype)) +
  coord_flip() +
  theme_few() +
  geom_point(position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(min = mean_audpc - sd_audpc, max = mean_audpc + sd_audpc), position = position_dodge(width = 0.4), width = 0.2)
```

@@

mix_gua <- lmer(
  audpc ~ genotype +
    (1 | exp/spike),
  data = audpc_gua, REML = FALSE
)
```

@@

library(emmeans)
means <- emmeans(mix_gua, ~ genotype)
cld(means)
```

@@

```{r}
Anova(mix_194)
library(emmeans)
means <- emmeans(mix_194, ~ genotype)
cld(means)
```

@@

```{r}
ec502 <- ec50 %>%
  group_by(isolate, species, genotype)%>%
  summarize(mean_ec50 = mean(ec50),
            sd_ec50 = sd(ec50)
            )
```

@@

library(viridis)
library(ggthemes)
ec502 %>%
  ggplot(aes(genotype, mean_ec50, color = species))+
  geom_jitter(width = 0.1)+
  #geom_errorbar(aes(min = mean_ec50 - sd_ec50, max = mean_ec50 + sd_ec50), width=0.2, position = position_dodge(width = 0.2))+
  theme_few()+
  theme(legend.position="right", legend.text=element_text(size=7, face = 'italic'))+
    ylim(0,1.8)+
 scale_color_viridis( discrete = TRUE)+
  labs(y = (expression(paste('EC'[50], ' (', mu,'g/ml)'))), x = "Trichothecene genotype", color="Species")+
  ggsave(here("figs", "ec50-new.png"), width=4.5, height=3)

```

>>>>

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(tidyverse)
library(here)
library(readxl)
library(viridis)
library(ggthemes)
library(lme4)
library(cowplot)
library(broom)
library(agricolae)
library(lattice)
library(emmeans)
library(car)
library(scales)
```

@@

```{r message=FALSE, warning=FALSE}
Anova(glmm_per)
```

@@

```{r}
plot(glmm_per, type = c("p", "smooth"))
qqmath(glmm_per, id = 0.05)
```

@@

```{r message=FALSE, warning=FALSE}
medias <- emmeans(glmm_per, ~ species_genotype * substrate)
med <- cld(medias, Letters = LETTERS, alpha = .05)

@@

This new `med` dataframe does not contain the two original variables we want to use to plot the data. Let's separate the `species_genotype` variable and create `genotype` and `species`.

@@

mgr <- read_excel(here("data", "all-data.xlsx"), "mycelia")

@@

```{r}
# 15 C
mgr15 <- mgr %>%
  filter(temperature == "15")

@@

# 30 C
mgr30 <- mgr %>%
  filter(temperature == "30")

@@

```{r message=FALSE, warning=FALSE}
spor1 <- spor %>%
  group_by(species, genotype, isolate) %>%
  summarize(mean_spor = mean(spores_ml))
spor2 <- spor1 %>%
  ggplot(aes(genotype, mean_spor, color = species)) +
  geom_jitter(width = 0.1, size = 3) +
  theme_few() +
  scale_color_viridis(discrete = TRUE) +
  theme(legend.position = c(1, 5), axis.text.x = element_text(angle = 0, hjust = 0.5, size = 7), legend.text = element_text(size = 7, face = "italic"), axis.title = element_text(size = 8)) +
  labs(x = "", y = "Macroconidia count (x 10.000)", color = "Species") +
  ylim(0, 5) +
  guides(colour = guide_legend(nrow = 2))
```

@@

grid5 <- plot_grid(mgr1, grid1, labels = c("A"), rel_heights = c(1, 1), ncol = 1, align = "hv")
ggsave(here("figs", "figure2.png"), grid5, width = 5, height = 5)

@@

### Visualize temporal

brs194 <- pathogen_194 %>%
  group_by(dai, genotype, species) %>%
  ggplot(aes(dai, mean_sev, color = species, shape = genotype, group = interaction(species, genotype))) +
  geom_point(position = position_dodge(width = 0.9)) +
  geom_line() +
  geom_errorbar(
    aes(min = mean_sev - sd_sev, max = mean_sev + sd_sev),
    width = 0.2, alpha = 0.3, position = position_dodge(width = 0.9)
  ) +
  theme_few() +
  ylim(0, 55) +
  xlim(0, 25) +
  theme(legend.position = "right", legend.text = element_text(size = 7, face = "italic")) +
  scale_color_viridis(discrete = TRUE) +
  labs(
    y = "FHB severity (%) ", x = "Days after inoculation",
    color = "species"
  )

brsgua <- pathogen_Gua %>%
  group_by(dai, genotype, species) %>%
  ggplot(aes(dai, mean_sev, color = species, shape = genotype, group = interaction(species, genotype))) +
  geom_point(position = position_dodge(width = 0.9)) +
  geom_line() +
  geom_errorbar(
    aes(min = mean_sev - sd_sev, max = mean_sev + sd_sev),
    width = 0.2, alpha = 0.3, position = position_dodge(width = 0.9)
  ) +
  theme_few() +
  theme(legend.position = "none") +
  scale_color_viridis(discrete = TRUE) +
  ylim(0, 55) +
  xlim(0, 25) +
  labs(
    y = "FHB severity (%) ", x = "Days after inoculation",
    color = "species"
  )

fig3 <- plot_grid(brsgua, brs194, labels = c("A", "B"), rel_widths = c(0.7, 1), ncol = 2, align = "hv")
ggsave(here("figs", "figure3.png"), fig3, width = 9, height = 4)

fig3
```

### Visualize AUDPC

@@

```{r}
audpc_194 %>%
  group_by(species, genotype) %>%
  summarize(
    mean_audpc = mean(audpc),
    sd_audpc = sd(audpc)
  ) %>%
  ggplot(aes(species, mean_audpc, color = genotype)) +
  coord_flip() +
  theme_few() +
  geom_point(position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(min = mean_audpc - sd_audpc, max = mean_audpc + sd_audpc), position = position_dodge(width = 0.4), width = 0.2)
```

@@

mix_gua <- lmer(
  audpc ~ genotype +
    (1 | exp / spike),
  data = audpc_gua, REML = FALSE
)
```

@@

means <- emmeans(mix_gua, ~ genotype)
cld(means)
```

@@

```{r}
Anova(mix_194)
means <- emmeans(mix_194, ~ genotype)
cld(means)
```

@@

```{r}
ec502 <- ec50 %>%
  group_by(isolate, species, genotype) %>%
  summarize(
    mean_ec50 = mean(ec50),
    sd_ec50 = sd(ec50)
  )
```

@@

```{r}
ec502 %>%
  ggplot(aes(genotype, mean_ec50, color = species)) +
  geom_jitter(width = 0.1) +
  # geom_errorbar(aes(min = mean_ec50 - sd_ec50, max = mean_ec50 + sd_ec50), width=0.2, position = position_dodge(width = 0.2))+
  theme_few() +
  theme(legend.position = "right", legend.text = element_text(size = 7, face = "italic")) +
  ylim(0, 1.8) +
  scale_color_viridis(discrete = TRUE) +
  labs(y = (expression(paste("EC"[50], " (", mu, "g/ml)"))), x = "Trichothecene genotype", color = "Species") +
  ggsave(here("figs", "ec50-new.png"), width = 4.5, height = 3)
```
